Regression

### 2018-02-06 paper/R/04_Modelresults.Rmd
minor changes

ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
dpi = 600)
```

@@

freq <- freq %>%
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic")
```

```{r}
p1 <- ggplot(freq, aes(reorder(topic_name, freq_diff), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

ggsave(plot = p1, filename = "../figs/topic_proportion_diff.png", device = "png",width = 8, height = 12,
dpi = 600)
```

@@

# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

@@

# ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

>>>>

#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
#dpi = 600)
```

@@

freq <- freq %>%
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic") %>%
  left_join(., frequency %>% mutate(topic_name = topic) %>%
              select(-topic),
            by = "topic_name")
```

```{r}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.y = element_blank(),
          #axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

p1 + p2

ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
dpi = 600)
```

@@

ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
dpi = 600)
```

@@

ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 7,
dpi = 600)
```
